### 2021-08-30 manuscript/methodology.tex

In theory, this method is bound to converge at $N$ iterations maximum, but in a later part of this work we show with numerical results that the convergence is much faster for the linear system we are solving.

@@

	\caption{Conjugate Gradient Least Square pseudocode \citep[][ p. 166]{aster2018parameter}.}
\label{al:cgls-algorithm}
\end{algorithm}

@@

In theory, this method is bound to converge at $N$ iterations maximum, but in a later part of this work we show with numerical results that the convergence is much faster for the linear system we are solving. Setting a minimum tolerance of the residuals is a good option to carry out this algorithm efficiently and still obtaining very good results. Another possibility is to set an invariance to the euclidian norm of residuals between iteractions, wich would increase algorithm runtime, but with smaller residuals. We chose the first option, as we achieve satisfatory results.

@@

In a $x$-\textit{oriented grid} $q$ and $p$ give the number of blocks ($Q = N_{y}$) and the number of elements of each block ($P = N_{x}$). They can be defined by the integer functions:
\begin{equation}
q(i, j) = \; l(i) - l(j)
\label{eq:q-x-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; k(i) - k(j) \: ,
\label{eq:p-x-oriented}
\end{equation}
where equations \ref{eq:l-x-oriented} and \ref{eq:k-x-oriented} describe $l(i)$ and $l(j)$ and $k(i)$ and $k(j)$, respectively. When using $y$-oriented grids, $q$ and $p$ still define the number of block and block elements, but $Q = N_{x}$ and $P = N_{y}$. Moreover, the integer functions changes to:
\begin{equation}
q(i, j) = \; k(i) - k(j) 
\label{eq:q-y-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; l(i) - l(j) \: ,
\label{eq:p-y-oriented}
\end{equation}
where equation \ref{eq:k-y-oriented} now defines $k(i)$ and $k(j)$ and equation \ref{eq:l-y-oriented} defines $l(i)$ and $l(j)$. Note that equations \ref{eq:q-x-oriented}, \ref{eq:p-x-oriented}, \ref{eq:q-y-oriented} and \ref{eq:q-y-oriented} differs from the ones presented in \cite{takahashi2020convolutional} by the absence of the module.

@@

Also differently for the symmetric sensitivity matrix described by \cite{takahashi2020convolutional}, the non-symmetric BTTB matrix cannot be reconstructed only by its first column. The construction of the matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) needs four columns: the first and last columns of the first column of blocks and the first and last columns of the last column of blocks. This has a physical implication in the equivalent layer which is not possible to use only one equivalent source to reprduce all elements of matrix $\mathbf{A}$, such as in the gravity case as demonstrared by \cite{takahashi2020convolutional}. Rather, in the magnetic case it takes four equivalent sources positioned at each corner of the equivalent layer. Figure \ref{fig:4_equivalent_sources} shows the positioning of the equivalent sources in a regular grid $N_x = 4$ $N_y = 3$ necessary to calculate the four columns capable of recover the matrix $\mathbf{A}$.

@@

If we consider that $c_{m} \, \frac{\mu_{0}}{4\pi}$, $\hat{\mathbf{F}}$ (equation \ref{eq:unit_vector_F}) and $\hat{\mathbf{h}}$ (equation\ref{eq:h_hat}) are constants multiplying the second derivatives $\mathbf{H}$ (equation \ref{eq:Hi}), the sensitivity matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is purely the sum of the components $H_{xx} + H_{xy} + H_{xz} + H_{xy} + H_{yy} + H_{yz} + H_{xz} + H_{yz} + H_{zz}$ multiplied by the respectives constants of each component. Thus, despite $\mathbf{A}$ not being a symmetric BTTB matrix, it can be in fact, written by calculating only the first column of these components.
In the next few sections we will describe each component $\mathbf{H}$ as its own matrix.

@@

\begin{equation}
	h^{yy}_{ij} = \frac{-1}{ \left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{3}{2}}} + 
	\frac{3 (\Delta l_{ij} \, \Delta y )^{2}}{\left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: 
	\label{eq:hyy_mag}
\end{equation}
and
\begin{equation}
	h^{zz}_{ij} = \frac{-1}{ \left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{3}{2}}} + 
	\frac{3 (\Delta z )^{2}}{\left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: ,
	\label{eq:hzz_mag}
\end{equation}
where $\Delta z = z_j - z_i$, $\Delta k_{ij} =k(i) - k(j)$ (equations \ref{eq:k-x-oriented} or \ref{eq:k-y-oriented}) and $\Delta l_{ij} = l(i) - l(j)$ (equations \ref{eq:l-x-oriented} or \ref{eq:l-y-oriented}).
The principal components $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ (equations \ref{eq:hxx_mag}, \ref{eq:hyy_mag} and \ref{eq:hzz_mag}, respectively) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are symmetric-Block-Toeplitz symmetric-Toeplitz-Block matrices. This means that $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ are Toeplitz and symmetric by its blocks and each of the blocks are symmetric Toeplitz matrices. 
For example, $\mathbf{H_{xx}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = 0, \dots, Q - 1$:
\begin{equation}
\mathbf{H_{xx}} = \begin{bmatrix}
\mathbf{H}^{0}_\mathbf{xx}  & \mathbf{H}^{1}_\mathbf{xx} & \cdots         & \mathbf{H}^{Q-1}_\mathbf{xx} \\
\mathbf{H}^{1}_\mathbf{xx}  & \mathbf{H}^{0}_\mathbf{xx} & \ddots         & \vdots           \\ 
\vdots           & \ddots         & \ddots         & \mathbf{H}^{1}_\mathbf{xx}   \\
\mathbf{H}^{Q-1}_\mathbf{xx} & \cdots         & \mathbf{H}^{1}_\mathbf{xx} & \mathbf{H}^{0}_\mathbf{xx}                
\end{bmatrix}_{N \times N} \: .
\label{eq:BTTB_Hxx}
\end{equation}
And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = 0, \dots, P - 1$:
\begin{equation}
\mathbf{H}^{q}_\mathbf{xx} = \{h^{q}_p\} = \begin{bmatrix}
h^{q}_{0}   & h^{q}_{1} & \cdots    & h^{q}_{P-1} \\
h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
\vdots      & \ddots    & \ddots    & h^{q}_{1}   \\
h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
\end{bmatrix}_{P \times P} \: .
\label{eq:Hxx_block}
\end{equation}
In a $x$-\textit{oriented grid} $Q = N_{x}$, $P = N_{y}$ and $q$ and $p$ can be defined by the functions:
\begin{equation}
q(i, j) = \; \mid l(i) - l(j) \mid
\label{eq:Hxx-q-x-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; \mid k(i) - k(j) \mid \quad ,
\label{eq:Hxx-p-x-oriented}
\end{equation}
where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are defined, respectively, by the following integer functions 
of the matrix indices $i$ and $j$:
\begin{equation}
q(i, j) = \; \mid k(i) - k(j) \mid 
\label{eq:Hxx-q-y-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; \mid l(i) - l(j) \mid \quad ,
\label{eq:Hxx-p-y-oriented}
\end{equation}
This struture can also describe matrices $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ in the same manner and they are identical to the structure of the gravity sensitivity matrix from \cite{takahashi2020convolutional}.

@@

The component $\mathbf{H_{xy}}$ (equation \ref{eq:hxy_mag}) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are skew symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block matrices. This means that $\mathbf{H_{xy}}$ is Toeplitz and skew symmetric by its blocks and each of the blocks are skew symmetric Toeplitz matrices. 
This way, matrix $\mathbf{H_{xy}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xy}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
\begin{equation}
	\mathbf{H_{xy}} = \begin{bmatrix}
		\mathbf{H}^{0}_\mathbf{xy}  & \mathbf{H}^{-1}_\mathbf{xy} & \cdots         & \mathbf{H}^{-Q+1}_\mathbf{xy} \\
		\mathbf{H}^{1}_\mathbf{xy}  & \mathbf{H}^{0}_\mathbf{xy} & \ddots         & \vdots           \\ 
		\vdots           & \ddots         & \ddots         & \mathbf{H}^{-1}_\mathbf{xy}   \\
		\mathbf{H}^{Q-1}_\mathbf{xy} & \cdots         & \mathbf{H}^{1}_\mathbf{xy} & \mathbf{H}^{0}_\mathbf{xy}                
	\end{bmatrix}_{N \times N} \: .
	\label{eq:BTTB_Hxy}
\end{equation}
And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = -P + 1, \dots, 0, \dots, P - 1$:
\begin{equation}
	\mathbf{H}^{q}_\mathbf{xy} =  \{h^{q}_p\} = \begin{bmatrix}
		h^{q}_{0}   & h^{q}_{-1} & \cdots    & h^{q}_{-P+1} \\
		h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
		\vdots      & \ddots    & \ddots    & h^{q}_{-1}   \\
		h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
	\end{bmatrix}_{P \times P} \: .
	\label{eq:Hxy_block}
\end{equation}
In a $x$-\textit{oriented grid} $Q = N_{x}$, $P = N_{y}$ and $q$ and $p$ can be defined by the functions:
\begin{equation}
	q(i, j) = \; l(i) - l(j) 
	\label{eq:Hxy-q-x-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \; k(i) - k(j) \quad ,
	\label{eq:Hxy-p-x-oriented}
\end{equation}
where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are defined, respectively, by the following integer functions 
of the matrix indices $i$ and $j$:
\begin{equation}
	q(i, j) = \;  k(i) - k(j)  
	\label{eq:Hxy-q-y-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \;  l(i) - l(j)  \quad ,
	\label{eq:Hxy-p-y-oriented}
\end{equation}
Important to clarify that in this case, as a skew symmetric matrix, the values of oposing diagonals have oposing signals, e.g., $\mathbf{H}^{-1}_\mathbf{xy} = -\mathbf{H}^{1}_\mathbf{xy}$ and $h^{q}_{-1} = -h^{q}_{1} $.

@@

The component $\mathbf{H_{xz}}$ (equation \ref{eq:hxz_mag}) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are skew symmetric-Block-Toeplitz symmetric-Toeplitz-Block matrices. This means that $\mathbf{H_{xz}}$ is Toeplitz and skew symmetric by its blocks and each of the blocks are symmetric Toeplitz matrices. 
Thus, matrix $\mathbf{H_{xz}}$ can be described by the \textit{block indice} $q$ that represent the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xz}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
\begin{equation}
	\mathbf{H_{xz}} = \begin{bmatrix}
		\mathbf{H}^{0}_\mathbf{xz}  & \mathbf{H}^{-1}_\mathbf{xz} & \cdots         & \mathbf{H}^{-Q+1}_\mathbf{xz} \\
		\mathbf{H}^{1}_\mathbf{xz}  & \mathbf{H}^{0}_\mathbf{xz} & \ddots         & \vdots           \\ 
		\vdots           & \ddots         & \ddots         & \mathbf{H}^{-1}_\mathbf{xz}   \\
		\mathbf{H}^{Q-1}_\mathbf{xz} & \cdots         & \mathbf{H}^{1}_\mathbf{xz} & \mathbf{H}^{0}_\mathbf{xz}                
	\end{bmatrix}_{N \times N} \: .
	\label{eq:BTTB_Hxz}
\end{equation}
And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = 0, \dots, P - 1$:
\begin{equation}
	\mathbf{H}^{q}_\mathbf{xz} =  \{h^{q}_p\} = \begin{bmatrix}
		h^{q}_{0}   & h^{q}_{1} & \cdots    & h^{q}_{P-1} \\
		h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
		\vdots      & \ddots    & \ddots    & h^{q}_{1}   \\
		h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
	\end{bmatrix}_{P \times P} \: .
	\label{eq:Hxz_block}
\end{equation}
In a $x$-\textit{oriented grid} $Q = N_{x}$, $P = N_{y}$ and $q$ and $p$ can be defined by the functions:
\begin{equation}
	q(i, j) = \; l(i) - l(j) 
	\label{eq:Hxz-q-x-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \; \mid k(i) - k(j) \mid \quad ,
	\label{eq:Hxz-p-x-oriented}
\end{equation}
where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are defined, respectively, by the following integer functions 
of the matrix indices $i$ and $j$:
\begin{equation}
	q(i, j) = \;  k(i) - k(j)  
	\label{eq:Hxz-q-y-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \; \mid l(i) - l(j) \mid \quad ,
	\label{eq:Hxz-p-y-oriented}
\end{equation}
In this case as a skew symmetric matrix by blocks, the values of oposing diagonals blocks have oposing signals, e.g., $\mathbf{H}^{-1}_\mathbf{xz} = -\mathbf{H}^{1}_\mathbf{xz}$ but each block is a symmetric matrix.

@@

As pointed earlier in this work, the main improvement inside the CGLS method (Algorithm \ref{al:cgls-algorithm}) for estimating the parameter vector $\hat{\mathbf{p}}$ (equation \ref{eq:estimated-p-parameter-space}) is to substitute the matrix-vector multiplication $\mathbf{A}^{\top} \mathbf{s}^{(0)}$ out of the loop and the two matrix-vector multiplications inside the loop at steps 3 an 6, $\mathbf{A} \, \mathbf{c}^{(it)}$ and $\mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$, that is necessary at each iteration and takes most of its runtime.

Our method consists in calculating the six first columns of the second derivatives of $\mathbf{H}$ (equation \ref{eq:Hi}) and embbed them into the first six columns of the block-circulant circulant-block (BCCB) matrices related to the $\mathbf{H}$ components. Thus, it is possible to calculate the first column of the BCCB matrix embbeded from matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) by multiplying each component with its respective constants and summing as shown in equation \ref{eq:aij_mag_expand}. In \cite{takahashi2020convolutional}, Appendix A, the authors demonstrated in details how to transform a symmetric BTTB matrix into a BCCB matrix $\mathbf{C}$. The process here is the same and that work can be referenced to achieve the same results.

>>>>

In theory, this method is bound to converge after at most  $N$ iterations, but in a later part of this work we show with numerical results that the convergence is much faster for the linear system we are solving.

@@

	\caption{Conjugate Gradient Least Square pseudocode \citep[][ p. 155]{aster2018parameter}.}
\label{al:cgls-algorithm}
\end{algorithm}

@@

Setting a minimum tolerance of the residuals is a good option to carry out this algorithm efficiently and still obtaining very good results. 
Another possibility is to set an invariance to the Euclidean norm of residuals between iteractions, wich would increase algorithm runtime, but with smaller residuals. 
We chose the first option, as we achieve satisfatory results.

@@

In a $x$-\textit{oriented grid} $q$ and $p$ give the number of blocks ($Q = N_{y}$) and the number of elements of each block ($P = N_{x}$). They can be defined by the integer functions:
\begin{equation}
q(i, j) = \; l(i) - l(j)
\label{eq:q-x-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; k(i) - k(j) \: ,
\label{eq:p-x-oriented}
\end{equation}
where equations \ref{eq:l-x-oriented} and \ref{eq:k-x-oriented} describe $l(i)$ and $l(j)$ and $k(i)$ and $k(j)$, respectively. When using $y$-oriented grids, $q$ and $p$ still define the number of block and block elements, but $Q = N_{x}$ and $P = N_{y}$. Moreover, the integer functions changes to:
\begin{equation}
q(i, j) = \; k(i) - k(j) 
\label{eq:q-y-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; l(i) - l(j) \: ,
\label{eq:p-y-oriented}
\end{equation}
where equation \ref{eq:k-y-oriented} now defines $k(i)$ and $k(j)$ and equation \ref{eq:l-y-oriented} defines $l(i)$ and $l(j)$. Note that equations \ref{eq:q-x-oriented}, \ref{eq:p-x-oriented}, \ref{eq:q-y-oriented} and \ref{eq:p-y-oriented} differs from the ones presented in \cite{takahashi2020convolutional} by the absence of the module.

@@

Also differently for the symmetric sensitivity matrix described by \cite{takahashi2020convolutional}, the non-symmetric BTTB matrix cannot be reconstructed only by its first column. The construction of the matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) needs four columns: the first and last columns of the first column of blocks and the first and last columns of the last column of blocks. This has a physical implication in the equivalent layer which is not possible to use only one equivalent source to reprduce all elements of matrix $\mathbf{A}$, such as in the gravity case as demonstrared by \cite{takahashi2020convolutional}. Rather, in the magnetic case it takes four equivalent sources positioned at each corner of the equivalent layer. Figure \ref{fig:4_equivalent_sources} shows the positioning of the equivalent sources in a regular grid $N_x = 4$
and $N_y = 3$ necessary to calculate the four columns capable of recover the matrix $\mathbf{A}$.

@@

In equation \ref{eq:aij_mag_expand}, $c_{m} \, \frac{\mu_{0}}{4\pi}$ is a constant.
If we consider that the components o the vectors 
$\hat{\mathbf{F}}$ (equation \ref{eq:unit_vector_F}) and $\hat{\mathbf{h}}$ (equation\ref{eq:h_hat}) are constants multiplying the second derivatives $\mathbf{H}$ (equation \ref{eq:Hi}); then, 
the sensitivity matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) is purely the sum of the components $H_{xx} + H_{xy} + H_{xz} + H_{xy} + H_{yy} + H_{yz} + H_{xz} + H_{yz} + H_{zz}$ multiplied by the respectives constants of each component. Thus, despite $\mathbf{A}$ not being a symmetric BTTB matrix, it can be in fact, written by calculating only the first column of these components.
In the next few sections we will describe each component $\mathbf{H}$ as its own matrix.

@@

\begin{equation}
	h^{yy}_{ij} = \frac{-1}{ \left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{3}{2}}} + 
	\frac{3 (\Delta l_{ij} \, \Delta y )^{2}}{\left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: 
	\label{eq:hyy_mag}
\end{equation}
and
\begin{equation}
	h^{zz}_{ij} = \frac{-1}{ \left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{3}{2}}} + 
	\frac{3 (\Delta z )^{2}}{\left[ 
		\left( \Delta k_{ij} \, \Delta x \right)^{2} + 
		\left( \Delta l_{ij} \, \Delta y \right)^{2} + 
		\left( \Delta z \right)^{2} \right]^{\frac{5}{2}}} \: ,
	\label{eq:hzz_mag}
\end{equation}
where $\Delta z = z_j - z_i$, $\Delta k_{ij} =k(i) - k(j)$ (equations \ref{eq:k-x-oriented} or \ref{eq:k-y-oriented}) and $\Delta l_{ij} = l(i) - l(j)$ (equations \ref{eq:l-x-oriented} or \ref{eq:l-y-oriented}).
The principal components $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ (equations \ref{eq:hxx_mag}, \ref{eq:hyy_mag} and \ref{eq:hzz_mag}, respectively) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are symmetric-Block-Toeplitz symmetric-Toeplitz-Block matrices. This means that $\mathbf{H_{xx}}$, $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ are Toeplitz and symmetric by its blocks and each of the blocks are symmetric Toeplitz matrices. 
For example, $\mathbf{H_{xx}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xx}$, $q = 0, \dots, Q - 1$:
\begin{equation}
\mathbf{H_{xx}} = \begin{bmatrix}
\mathbf{H}^{0}_\mathbf{xx}  & \mathbf{H}^{1}_\mathbf{xx} & \cdots         & \mathbf{H}^{Q-1}_\mathbf{xx} \\
\mathbf{H}^{1}_\mathbf{xx}  & \mathbf{H}^{0}_\mathbf{xx} & \ddots         & \vdots           \\ 
\vdots           & \ddots         & \ddots         & \mathbf{H}^{1}_\mathbf{xx}   \\
\mathbf{H}^{Q-1}_\mathbf{xx} & \cdots         & \mathbf{H}^{1}_\mathbf{xx} & \mathbf{H}^{0}_\mathbf{xx}                
\end{bmatrix}_{N \times N} \: .
\label{eq:BTTB_Hxx}
\end{equation}
And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = 0, \dots, P - 1$:
\begin{equation}
\mathbf{H}^{q}_\mathbf{xx} = \{h^{q}_p\} = \begin{bmatrix}
h^{q}_{0}   & h^{q}_{1} & \cdots    & h^{q}_{P-1} \\
h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
\vdots      & \ddots    & \ddots    & h^{q}_{1}   \\
h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
\end{bmatrix}_{P \times P} \: .
\label{eq:Hxx_block}
\end{equation}
In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_{x}$ and $q$ and $p$ can be defined by the functions:
\begin{equation}
q(i, j) = \; \mid l(i) - l(j) \mid
\label{eq:Hxx-q-x-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; \mid k(i) - k(j) \mid \quad ,
\label{eq:Hxx-p-x-oriented}
\end{equation}
where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are defined, respectively, by the following integer functions 
of the matrix indices $i$ and $j$:
\begin{equation}
q(i, j) = \; \mid k(i) - k(j) \mid 
\label{eq:Hxx-q-y-oriented}
\end{equation}
and
\begin{equation}
p(i, j) = \; \mid l(i) - l(j) \mid \quad ,
\label{eq:Hxx-p-y-oriented}
\end{equation}
This struture can also describe matrices $\mathbf{H_{yy}}$ and $\mathbf{H_{zz}}$ in the same manner and they are identical to the structure of the gravity sensitivity matrix from \cite{takahashi2020convolutional}.

@@

The component $\mathbf{H_{xy}}$ (equation \ref{eq:hxy_mag}) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are skew symmetric-Block-Toeplitz skew symmetric-Toeplitz-Block matrices. This means that $\mathbf{H_{xy}}$ is Toeplitz and skew symmetric by its blocks and each of the blocks are skew symmetric Toeplitz matrices. 
This way, matrix $\mathbf{H_{xy}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xy}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
\begin{equation}
	\mathbf{H_{xy}} = \begin{bmatrix}
		\mathbf{H}^{0}_\mathbf{xy}  & \mathbf{H}^{-1}_\mathbf{xy} & \cdots         & \mathbf{H}^{-Q+1}_\mathbf{xy} \\
		\mathbf{H}^{1}_\mathbf{xy}  & \mathbf{H}^{0}_\mathbf{xy} & \ddots         & \vdots           \\ 
		\vdots           & \ddots         & \ddots         & \mathbf{H}^{-1}_\mathbf{xy}   \\
		\mathbf{H}^{Q-1}_\mathbf{xy} & \cdots         & \mathbf{H}^{1}_\mathbf{xy} & \mathbf{H}^{0}_\mathbf{xy}                
	\end{bmatrix}_{N \times N} \: .
	\label{eq:BTTB_Hxy}
\end{equation}
And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = -P + 1, \dots, 0, \dots, P - 1$:
\begin{equation}
	\mathbf{H}^{q}_\mathbf{xy} =  \{h^{q}_p\} = \begin{bmatrix}
		h^{q}_{0}   & h^{q}_{-1} & \cdots    & h^{q}_{-P+1} \\
		h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
		\vdots      & \ddots    & \ddots    & h^{q}_{-1}   \\
		h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
	\end{bmatrix}_{P \times P} \: .
	\label{eq:Hxy_block}
\end{equation}
In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_{x}$ and $q$ and $p$ can be defined by the functions:
\begin{equation}
	q(i, j) = \; l(i) - l(j) 
	\label{eq:Hxy-q-x-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \; k(i) - k(j) \quad ,
	\label{eq:Hxy-p-x-oriented}
\end{equation}
where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are defined, respectively, by the following integer functions 
of the matrix indices $i$ and $j$:
\begin{equation}
	q(i, j) = \;  k(i) - k(j)  
	\label{eq:Hxy-q-y-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \;  l(i) - l(j)  \quad ,
	\label{eq:Hxy-p-y-oriented}
\end{equation}
Important to clarify that in this case, as a skew symmetric matrix, the values of oposing diagonals have oposing signals, e.g., $\mathbf{H}^{-1}_\mathbf{xy} = -\mathbf{H}^{1}_\mathbf{xy}$ and $h^{q}_{-1} = -h^{q}_{1} $.

@@

The component $\mathbf{H_{xz}}$ (equation \ref{eq:hxz_mag}) of matrix $\mathbf{H}$ (equation \ref{eq:Hi}) are skew symmetric-Block-Toeplitz symmetric-Toeplitz-Block matrices. This means that $\mathbf{H_{xz}}$ is Toeplitz and skew symmetric by its blocks and each of the blocks are symmetric Toeplitz matrices. 
Thus, matrix $\mathbf{H_{xz}}$ can be described by the \textit{block index} $q$ that represents the block diagonals of this matrix as a grid of $Q \times Q$ blocks $\mathbf{H}^{q}_\mathbf{xz}$, $q = -Q + 1, \dots, 0, \dots, Q - 1$:
\begin{equation}
	\mathbf{H_{xz}} = \begin{bmatrix}
		\mathbf{H}^{0}_\mathbf{xz}  & \mathbf{H}^{-1}_\mathbf{xz} & \cdots         & \mathbf{H}^{-Q+1}_\mathbf{xz} \\
		\mathbf{H}^{1}_\mathbf{xz}  & \mathbf{H}^{0}_\mathbf{xz} & \ddots         & \vdots           \\ 
		\vdots           & \ddots         & \ddots         & \mathbf{H}^{-1}_\mathbf{xz}   \\
		\mathbf{H}^{Q-1}_\mathbf{xz} & \cdots         & \mathbf{H}^{1}_\mathbf{xz} & \mathbf{H}^{0}_\mathbf{xz}                
	\end{bmatrix}_{N \times N} \: .
	\label{eq:BTTB_Hxz}
\end{equation}
And each diagonal of the blocks are represented by $P \times P$ elements $h^{q}_{p}$, $p = 0, \dots, P - 1$:
\begin{equation}
	\mathbf{H}^{q}_\mathbf{xz} =  \{h^{q}_p\} = \begin{bmatrix}
		h^{q}_{0}   & h^{q}_{1} & \cdots    & h^{q}_{P-1} \\
		h^{q}_{1}   & h^{q}_{0} & \ddots    & \vdots           \\ 
		\vdots      & \ddots    & \ddots    & h^{q}_{1}   \\
		h^{q}_{P-1} & \cdots    & h^{q}_{1} & h^{q}_{0}                 
	\end{bmatrix}_{P \times P} \: .
	\label{eq:Hxz_block}
\end{equation}
In a $x$-\textit{oriented grid} $Q = N_{y}$, $P = N_{x}$ and $q$ and $p$ can be defined by the functions:
\begin{equation}
	q(i, j) = \; l(i) - l(j) 
	\label{eq:Hxz-q-x-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \; \mid k(i) - k(j) \mid \quad ,
	\label{eq:Hxz-p-x-oriented}
\end{equation}
where $l(i)$ and $l(j)$ are defined by equation \ref{eq:l-x-oriented} 
and $k(i)$ and $k(j)$ are defined by equation \ref{eq:k-x-oriented}.
For $y$-oriented grids, $Q = N_{x}$, $P = N_{y}$ and the block indices
$q$ and $p$ are defined, respectively, by the following integer functions 
of the matrix indices $i$ and $j$:
\begin{equation}
	q(i, j) = \;  k(i) - k(j)  
	\label{eq:Hxz-q-y-oriented}
\end{equation}
and
\begin{equation}
	p(i, j) = \; \mid l(i) - l(j) \mid \quad ,
	\label{eq:Hxz-p-y-oriented}
\end{equation}
In this case as a skew symmetric matrix by blocks, the values of oposing diagonals blocks have oposing signals, e.g., $\mathbf{H}^{-1}_\mathbf{xz} = -\mathbf{H}^{1}_\mathbf{xz}$ but each block is a symmetric matrix.

@@

As pointed earlier in this work, the main improvement inside the CGLS method (Algorithm \ref{al:cgls-algorithm}) for estimating the parameter vector $\hat{\mathbf{p}}$ (equation \ref{eq:estimated-p-parameter-space}) is to substitute the matrix-vector multiplication $\mathbf{A}^{\top} \mathbf{s}^{(0)}$ out of the loop and the two matrix-vector multiplications inside the loop at steps 3 an 6, $\mathbf{A} \, \mathbf{c}^{(it)}$ and $\mathbf{A}^{\top} \, \mathbf{s}^{(it + 1)}$.
The latter two matrix-vector multiplications are accomplished at each iteration, thus taking most of CGLS method runtime.

Our method consists in calculating the six first columns of the second derivatives of $\mathbf{H}$ (equation \ref{eq:Hi}) and embedding them into the first six columns of the block-circulant circulant-block (BCCB) matrices related to the $\mathbf{H}$ components. Thus, it is possible to calculate the first column of the BCCB matrix embbeded from matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) by multiplying each component with its respective constants and summing as shown in equation \ref{eq:aij_mag_expand}. In \cite{takahashi2020convolutional}, Appendix A, the authors demonstrated in details how to transform a symmetric BTTB matrix into a BCCB matrix $\mathbf{C}$. The process here is the same and that work can be referenced to achieve the same results.
